fdcoexist

### 2018-12-12 meta_simulations.Rmd
Compare SR with diff. A, k, and B/A

    all_simuls = apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]])
    #     %>%
    #         landscape_df(all_cor[[given_row[["cor_level"]]]],
    #                      trait_scenarios[[given_row[["scenario"]]]],
    #                      time = 150) %>%
    #         inner_join(all_cor[[given_row[["cor_level"]]]] %>%
    #                        as.data.frame() %>%
    #                        rownames_to_column("species"),
    #                    by = "species") %>%
    #         group_by(patch) %>%
    #         mutate(rel_abund = N/sum(N)) %>%
    #         ungroup() %>%
    #         mutate(compet_status = given_row[["compet_status"]],
    #                env_width     = given_row[["env_width"]],
    #                cor_level     = given_row[["cor_level"]],
    #                scenario      = given_row[["scenario"]],
    #                seed_number = seed_number) %>%
    #         select(seed_number, compet_status, env_width, cor_level, scenario,
    #                everything())
    })
    # %>%
    #     bind_rows() %>%
    #     filter(N != 0) %>%  # Take out absent species
    #     mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
    #     mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
    #            patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    #     group_by(seed_number, compet_status, env_width, cor_level, scenario,
    #              patch) %>%
    #     summarise(trait1_cwm  = sum(trait1_cwm),
    #               trait2_cwm  = sum(trait2_cwm),
    #               trait3_cwm  = sum(trait3_cwm),
    #               trait1_var  = var(trait1),
    #               trait2_var  = var(trait2),
    #               trait3_var  = var(trait3),
    #               patch_optim = unique(patch_optim))

    list(simul = all_simuls, trait = uncor_traits)
}
# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

>>>>

    all_simuls = apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]])
    })

    list(simul = all_simuls, trait = uncor_traits)
}

meta_simul_A_B_and_k = function(seed_number, given_k = k, given_A = A,
                                given_B_over_A = B/A) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    all_cor = list(uncor = uncor_traits)

    all_compet = list(compet = list(A = given_A, B = given_A * given_B_over_A))

    our_scenars = list(
    R50A50   = data.frame(trait = paste0("trait", 1:3),
                          growth_weight = c(0.5, 0.5, 0),
                          compet_weight = c(0,   0.5, 0.5)))

    all_facets = expand.grid(compet_status = names(all_compet),
                             env_width     = names(all_env),
                             cor_level     = names(all_cor),
                             scenario      = names(our_scenars))

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 dist_power = 2,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(species_rich = sum(N > 0),
                  trait1_cwm   = sum(trait1_cwm),
                  trait2_cwm   = sum(trait2_cwm),
                  trait3_cwm   = sum(trait3_cwm),
                  trait1_var   = var(trait1),
                  trait2_var   = var(trait2),
                  trait3_var   = var(trait3),
                  patch_optim  = unique(patch_optim))
}
# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

## Coexistence plot depending on A, B/A and k

```{r param_space_simuls}
list_A = 10^-(seq(2, 6, length.out = 10))
list_k = seq(1, 1.5, length.out = 10)
list_B_over_A = 10^seq(0, 4, length.out = 10)

var_a_var_k_var_ba = cross(list(run_n = seq(1), A = list_A, k = list_k,
                         B_over_A = list_B_over_A)) %>%
    future_map(function(x) {
    devtools::load_all()

    meta_simul_A_B_and_k(x$run_n, x$k, x$A, x$B_over_A) %>%
        mutate(k = x$k, A = x$A, B_over = x$B_over_A)
}, .progress = TRUE)
tictoc::toc()

var_ba_df = bind_rows(var_a_var_k_var_ba)
```

```{r interactive_species_rich_plot}
library("plotly")

var_ba_df %>%
    filter(patch == "patches13", species_rich > 0) %>%
    plot_ly(x = ~k, y = ~A, z = ~B_over, color = ~species_rich,
            text = ~paste("SR: ", species_rich)) %>%
    add_markers() %>%
    layout(scene = list(xaxis = list(title = ),
                        yaxis = list(title = 'A (interspecific competition)',
                                     type = "log"),
                        zaxis = list(title = 'B/A (ratio intra/inter)',
                                     type = "log")))
```

```{r biplot_of_parameters_richness}
plot_k_A = var_ba_df %>%
    filter(patch %in% paste0("patches", c(1, 13))) %>%
    ggplot(aes(k, A)) +
    stat_summary_2d(aes(z = species_rich), fun = "mean", geom = "raster") +
    facet_wrap(~patch) +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "A (interspecific competition)",
         fill = "Species Richness\n(at t = 150)",
         subtitle = "Average Richness over all values of B/A") +
    theme(legend.position = "top")

plot_A_BA = var_ba_df %>%
    filter(patch %in% paste0("patches", c(1, 13))) %>%
    ggplot(aes(A, B_over)) +
    stat_summary_2d(aes(z = species_rich), fun = "mean", geom = "raster") +
    facet_wrap(~patch) +
    scale_fill_viridis_c() +
    scale_x_log10() +
    scale_y_log10() +
    labs(x = "A (interspecific competition)",
         y = "B/A (ratio intra/inter)",
         fill = "Species Richness\n(at t = 150)",
         subtitle = "Average Richness over all values of k") +
    theme(legend.position = "top")

plot_k_BA = var_ba_df %>%
    filter(patch %in% paste0("patches", c(1, 13))) %>%
    ggplot(aes(k, B_over)) +
    stat_summary_2d(aes(z = species_rich), fun = "mean", geom = "raster") +
    facet_wrap(~patch) +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "B/A (ratio intra/inter)",
         fill = "Species Richness\n(at t = 150)",
         subtitle = "Average Richness over all values of A") +
    theme(legend.position = "top")

plot_grid(plot_k_A, plot_A_BA, plot_k_BA, nrow = 3)
```

```{r biplot_with_R2_and_slope_values}
var_ba_r2 = var_ba_df %>%
    ungroup() %>%
    filter(!is.nan(trait2_cwm)) %>%
    nest(-k, -A,-B_over, -seed_number, -scenario) %>%
    mutate(data = data %>%
               map(~.x %>%
                       gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
                       group_by(cwm_name, add = TRUE) %>%
                       do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
                       ungroup() %>%
                       mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
                       unnest(mod_glance))) %>%
    unnest(data) %>%
    filter(cwm_name == "trait2_cwm")

var_ba_slope = var_ba_df %>%
    ungroup() %>%
    filter(!is.nan(trait2_cwm)) %>%
    nest(-k, -A,-B_over, -seed_number, -scenario) %>%
    mutate(data = data %>%
               map(~.x %>%
                       gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
                       group_by(cwm_name, add = TRUE) %>%
                       do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
                       ungroup() %>%
                       mutate(mod_glance = lapply(mod_cwm_env, broom::tidy)) %>%
                       unnest(mod_glance))) %>%
    unnest(data) %>%
    filter(cwm_name == "trait2_cwm") %>%
    filter(term == "patch_optim")

# Plotting R-squared
plot_k_A_r2 = var_ba_r2 %>%
    ggplot(aes(k, A)) +
    stat_summary_2d(aes(z = adj.r.squared), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "A (interspecific competition)",
         fill = "CWM <-> Env. R^2",
         subtitle = "Average R-squared over all values of B/A") +
    theme(legend.position = "top")

plot_A_BA_r2 = var_ba_r2 %>%
    ggplot(aes(A, B_over)) +
    stat_summary_2d(aes(z = adj.r.squared), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_x_log10() +
    scale_y_log10() +
    labs(x = "A (interspecific competition)",
         y = "B/A (ratio intra/inter)",
         fill = "CWM <-> Env. R^2",
         subtitle = "Average R-squared over all values of k") +
    theme(legend.position = "top")

plot_k_BA_r2 = var_ba_r2 %>%
    ggplot(aes(k, B_over)) +
    stat_summary_2d(aes(z = adj.r.squared), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "B/A (ratio intra/inter)",
         fill = "CWM <-> Env. R^2",
         subtitle = "Average R-squared over all values of A") +
    theme(legend.position = "top")

# Plotting CWM <-> Env. Slope
plot_k_A_slope = var_ba_slope %>%
    ggplot(aes(k, A)) +
    stat_summary_2d(aes(z = estimate), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "A (interspecific competition)",
         fill = "CWM <-> Env. Slope",
         subtitle = "Average Slope over all values of B/A") +
    theme(legend.position = "top")

plot_A_BA_slope = var_ba_slope %>%
    ggplot(aes(A, B_over)) +
    stat_summary_2d(aes(z = estimate), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_x_log10() +
    scale_y_log10() +
    labs(x = "A (interspecific competition)",
         y = "B/A (ratio intra/inter)",
         fill = "CWM <-> Env. Slope",
         subtitle = "Average Slope over all values of k") +
    theme(legend.position = "top")

plot_k_BA_slope = var_ba_slope %>%
    ggplot(aes(k, B_over)) +
    stat_summary_2d(aes(z = estimate), fun = "mean", geom = "raster") +
    scale_fill_viridis_c() +
    scale_y_log10() +
    labs(x = "k (maximum growth rate)",
         y = "B/A (ratio intra/inter)",
         fill = "CWM <-> Env. Slope",
         subtitle = "Average Slope over all values of A") +
    theme(legend.position = "top")

plot_grid(plot_k_A_r2,
          plot_k_A_slope,
          plot_A_BA_r2,
          plot_A_BA_slope,
          plot_k_BA_r2,
          plot_k_BA_slope,
          nrow = 3)
```

### 2018-12-12 paper_simulations.Rmd
Compare SR with diff. A, k, and B/A

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 500  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

# Competition + Dispersion coefficients
B = 2e-4 # Scalar for intraspecific competition
A = 1.6e-4 # Alpha scalar
d = 0.0 # Dispersal percentage

>>>>

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

# Competition + Dispersion coefficients
B = 2e-4 # Scalar for intraspecific competition
A = 2e-4 # Alpha scalar
d = 0.0 # Dispersal percentage
